% ============================================================
% TÀI LIỆU THAM KHẢO
% ============================================================
\clearpage
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\label{chap:references}

\begin{thebibliography}{99}
\sloppy

\bibitem{busso2008}
C. Busso, M. Bulut, C.-C. Lee, A. Kazemzadeh, E. Mower, S. Kim, J. N. Chang, S. Lee, and S. S. Narayanan,
``IEMOCAP: Interactive Emotional Dyadic Motion Capture Database,''
\textit{Language Resources and Evaluation}, vol. 42, no. 4, pp. 335--359, 2008.
\\ \url{https://sail.usc.edu/iemocap/}

\bibitem{krizhevsky2012}
A. Krizhevsky, I. Sutskever, and G. E. Hinton,
``ImageNet Classification with Deep Convolutional Neural Networks,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 25, 2012.
\\ \url{https://papers.nips.cc/paper/4824-imagenet-classification-with-deep-convolutional-neural-networks.pdf}

\bibitem{he2016}
K. He, X. Zhang, S. Ren, and J. Sun,
``Deep Residual Learning for Image Recognition,''
in \textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 770--778, 2016.
\\ \url{https://arxiv.org/abs/1512.03385}

\bibitem{huang2017}
G. Huang, Z. Liu, L. Van Der Maaten, and K. Q. Weinberger,
``Densely Connected Convolutional Networks,''
in \textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 4700--4708, 2017.
\\ \url{https://arxiv.org/abs/1608.06993}

\bibitem{tan2019}
M. Tan and Q. V. Le,
``EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks,''
in \textit{International Conference on Machine Learning (ICML)}, pp. 6105--6114, 2019.
\\ \url{https://arxiv.org/abs/1905.11946}

\bibitem{sandler2018}
M. Sandler, A. Howard, M. Zhu, A. Zhmoginov, and L.-C. Chen,
``MobileNetV2: Inverted Residuals and Linear Bottlenecks,''
in \textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 4510--4520, 2018.
\\ \url{https://arxiv.org/abs/1801.04381}

\bibitem{lin2017}
T.-Y. Lin, P. Goyal, R. Girshick, K. He, and P. Doll\'{a}r,
``Focal Loss for Dense Object Detection,''
in \textit{IEEE International Conference on Computer Vision (ICCV)}, pp. 2980--2988, 2017.
\\ \url{https://arxiv.org/abs/1708.02002}

\bibitem{zhang2018}
H. Zhang, M. Cissé, Y. N. Dauphin, and D. Lopez-Paz,
``mixup: Beyond Empirical Risk Minimization,''
in \textit{International Conference on Learning Representations (ICLR)}, 2018.
\\ \url{https://arxiv.org/abs/1710.09412}

\bibitem{deng2009}
J. Deng, W. Dong, R. Socher, L.-J. Li, K. Li, and L. Fei-Fei,
``ImageNet: A Large-Scale Hierarchical Image Database,''
in \textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 248--255, 2009.

\bibitem{paszke2019}
A. Paszke, S. Gross, F. Massa, A. Lerer, J. Bradbury, G. Chanan, T. Killeen, Z. Lin, N. Gimelshein, L. Antiga, A. Desmaison, A. Kopf, E. Yang, Z. DeVito, M. Raison, A. Tejani, S. Chilamkurthy, B. Steiner, L. Fang, J. Bai, and S. Chintala,
``PyTorch: An Imperative Style, High-Performance Deep Learning Library,''
in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 32, 2019.

\bibitem{mcfee2015}
B. McFee, C. Raffel, D. Liang, D. P. W. Ellis, M. McVicar, E. Battenberg, and O. Nieto,
``librosa: Audio and Music Signal Analysis in Python,''
in \textit{Proceedings of the 14th Python in Science Conference (SciPy)}, pp. 18--25, 2015.

\bibitem{el2011}
M. El Ayadi, M. S. Kamel, and F. Karray,
``Survey on Speech Emotion Recognition: Features, Classification Schemes, and Databases,''
\textit{Pattern Recognition}, vol. 44, no. 3, pp. 572--587, 2011.

\bibitem{schuller2018}
B. W. Schuller,
``Speech Emotion Recognition: Two Decades in a Nutshell, Benchmarks, and Ongoing Trends,''
\textit{Communications of the ACM}, vol. 61, no. 5, pp. 90--99, 2018.

\bibitem{dang2023emix}
A. Dang, T. H. Vu, L. D. Nguyen, and J.-C. Wang,
``EMix: A Data Augmentation Method for Speech Emotion Recognition,''
in \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP)}, pp. 1--5, 2023.
\\ \url{https://ieeexplore.ieee.org/document/10096789}

\end{thebibliography}
